### 2019-02-12 appendix_1.tex
fixes on interarrival distances
fixing constraints to capacity from arot and lti

\clearpage
\chapter{Inter-arrival time and distance separation}\label{app:time_and_dist_sep}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.0\textwidth]{graphics/fig_best_CC_from_HM_pairs_time_sep.png}
    \caption[AROT and LTI of C-C pairs from ICAO H-M pairs on RWY~19]{AROT and landing time intervals of C-C pairs originating from ICAO H-M pairs for RWY-19 during the summer season. The dashed red line indicates the RECAT-EU reference time separation for the C-C pairs.}
    \label{fig:best_CC_from_HM_pairs_time_sep}
\end{figure}

>>>>

\clearpage
\chapter{Landing time interval and AROT}\label{app:lti_and_arot}

@@
